Algebraic properties of CFT coset construction and Schramm-Loewner evolution

### 2011-08-21 AffineLieAlgebras/SLE/talk.tex

\documentclass[12pt]{article}
\usepackage{amssymb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{amsmath}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}

\title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
\author{A A Nazarov$^{1,2}$\\
  {\small $^1$ Theoretical Department, SPb State University}\\
  {\small 198904, Sankt-Petersburg, Russia}\\
  {\small$^{2}$ Chebyshev Laboratory,}\\
  {\small Department of Mathematics and Mechanics, SPb State University}\\
  {\small 199178, Saint-Petersburg, Russia}\\
  {\small email: antonnaz@gmail.com}}

\maketitle

\begin{abstract}
  Schramm-Loewner evolution appears naturally as the scaling limit of interfaces in lattice models at critical point. Critical behavior of these models can be described by minimal models of conformal field theory.

  SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT. Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.

  Minimal models can be obtained from WZNW models by coset construction. Then it is natural to study SLE with additional Brownian motion on coset space $G/H$. We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables. 
\end{abstract}

\section{Introduction}
\subsection{Schramm-Loewner evolution}
To remind of Schramm-Loewner evolution we first describe simple example.

Consider Ising model on triangular lattice on upper half plane (see Fig. \ref{fig:sle}). We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half. Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.

\begin{figure}[h]
  \centering{
    \includegraphics[height=25mm]{explore.pdf}
    \caption{SLE -- continuous limit of interfaces}}
  \label{fig:sle}
\end{figure}

Next we consider continuous limit of lattice model. Interface in random configuration of the model tends to random curve. We can think of this curve as of trace of stochastic process which satisfy some stochastic equation.

In papers [Smirnov, Schramm ... ] it was shown that this equation is
\begin{equation*}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} \quad \text{or} \quad       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}
\end{equation*}
The stochastic process which satisfy this equation is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.

Here $g_{t}(z)$ is a conformal map from $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$ to $\mathbb{H}$ (see Fig. \ref{fig:sle2}).
\begin{figure}[h]
  \centering{
    \includegraphics[width=50mm]{loewner.pdf}
    \caption{Conformal map}}
  \label{fig:sle2}
\end{figure}

Schramm-Loewner evolution provides conformally-invariant probability measure on trajectories $\gamma_{t}$ in $\mathbb{H}$.

\subsection{Correspondence between SLE and minimal models of CFT}

Now we can look at the observables in the presence of SLE trace. Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace up to some time $t$ multiplied by the probability of this trajectory.

Consider lattice observable $\mathcal{O}$, then it expectation value can be calculated as
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
\end{equation*}
Since lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.

In continuous limit lattice observable tends to CFT correlation function. Since we consider the theory with the boundary, CFT correlation function has following form:
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
\end{equation*}
We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$. Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.  We can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:

\begin{equation}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}

Now we want to consider evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
\end{equation*}
For transformation of primary fields $\phi_{\lambda_{i}}$ we have 
\begin{equation}
  \label{eq:2}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\phi_{\lambda_{i}}(w_{i}) 
\end{equation}
We denote generator of this transform by $\mathcal{G}_{i}$.

Continuous limit in critical point leads to CFT correlation function

Now for expectation value of martingale we have this expression.
\begin{equation*}
  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad \mathbb{E}\left[d \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
\end{equation*}

Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
\begin{equation*}
  \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
    \mathcal{F}_{\mathbb{H}_{t}}\right]=\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\mathbb{E}\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
\end{equation*}
Then use explicit form of conformal map and obtain
\begin{equation*}
  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
\end{equation*}

We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
\begin{equation*}
  (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0 \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
\end{equation*}
We can see that it can be rewritten as the action of Virasoro generators. Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state. 
In case of minimal model we can see that boundary condition chaining operator is primary field $\phi_{1,2}$ or $\phi_{2,1}$.

\section{SLE and WZNW models}
\label{sec:sle-wzw-models}
Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model.
\subsection{WZNW models}

 The action for this model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some Lie group $G$:
\begin{multline}
  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
  \\
  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
\end{multline}
The first term is just non-linear sigma-model.

 Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$. The second term is written in terms of continuation from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary. Since this continuation is non-unique we get the requirement for $k$ to be integer.

Currents of this model have following form:
  \begin{eqnarray}
    J(z)= -k \partial_zg g^{-1}
    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
  \end{eqnarray}

Model possess gauge invariance under gauge transformations:
  \begin{equation*}
    g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z),
  \end{equation*}
  where $\Omega,\;\bar \Omega \in G$.
Here $\Omega$ and $\bar \Omega$ are independent.

If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities:
  \begin{equation}
    \label{eq:87}
    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
  \end{equation}

 Then we can get operator product expansion for currents. 
 \begin{equation}
   \label{eq:3}
   <J\phi>\sim \dots
 \end{equation}

If we expand currents to modes
\begin{equation*}
  J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n 
\end{equation*}
and use operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
\begin{equation}
  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} 
\end{equation}

This model has conformal invariance which can be seen from 
Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
\begin{equation}
  \label{eq:4}
  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}:
\end{equation}

Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$.

Its commutation relations are
  \begin{equation}
    \label{eq:92}
    \begin{aligned}
      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
    \end{aligned}
  \end{equation}

Primary fields  $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
  \begin{equation*}
    \begin{aligned}
      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
    \end{aligned}
  \end{equation*}

\subsection{SLE and WZNW models}
Now we want to study Schramm-Loewner evolution in WZNW-models.

Similarly to minimal models we consider observable
\begin{equation*}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
\end{equation*}
Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
\begin{equation*}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
\end{equation*}

Consider evolution from $t$ to $t+dt$.
First factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.

 For fields we have
\begin{equation*}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})
\end{equation*}
When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}:
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
\end{equation*}
Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions.

\subsection{SLE martingales in WZNW models}
We use Ito calculus to get the equation from martingale condition:
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0
\end{equation*}
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
\end{equation*}
Again we can rewrite it as algebraic requirement for  field  which 
correspond to boundary condition changing operator.
\begin{equation*}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
\end{equation*}
is level two null state and if we act on this state with raising operators we should get zero.
\begin{equation*}
  J^{a}_{1} \left|\psi\right>=0, J^{a}_{2}\left|\psi\right>=0.
\end{equation*}
 We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation.

We can see that $\kappa+\tau h^{v}=4$ and it is possible to derive additional relations connecting $\kappa, \tau, k$:
\begin{equation*}
  \kappa=\frac{2(h^{v}-2k)}{2h_{\Lambda}h^{v}-k},\quad \tau=\frac{8 h_{\Lambda}-2}{2h_{\Lambda}h^{v}-k}  \quad\text{for}\; k\neq 2h_{\Lambda}h^{v}
\end{equation*}
 Also we get some constraints on possible boundary condition changing operators. 
To get complete classification use Knizhnik-Zamolodchikov equations.

\section{Coset models}
\label{sec:coset-models}

\subsection{Gauged WZNW-models and coset construction}
Add gauge fields $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
\begin{multline*}
  S(g,A)=S_{WZNW}(g)+\\
  \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
\end{multline*}

Now current is
\begin{equation*}
  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
\end{equation*}

From Ward identities we get
\begin{equation*}
  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
\end{equation*}
Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$.
%% Commutation relations for current components are preserved.

Algebraic structure is connected with two affine Lie algebras $\gfh, \afh: \afh\subset\gfh$.

Virasoro generators are given by difference of Sugawara expressions:
\begin{equation*}
  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
\end{equation*}

\subsection{Primary fields}

Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. But some pairs are equivalent. This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that $h_{J}-h_{\tilde{J}}=0$.

Conformal weight of primary field
\begin{multline}
  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
  \left|\phi_{\lambda}\right>=\\
  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
\end{multline}

%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.

It is possible to obtain analogues of KZ-equations:
\begin{equation*}
  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{v}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{v}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
\end{equation*}

\subsection{SLE on coset space}
For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
\end{equation*}
%% \begin{equation*}
%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
%% \end{equation*}

and get martingale condition
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
\end{equation*}

which can be rewritten as the requirement for
\begin{equation*}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
\end{equation*}
to be level two null-field.

\subsection{Parafermions}
$\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.

Parafermionic field decomposes as
\begin{equation*}
  \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
\end{equation*}
where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.

For parafermionic current we have
\begin{equation*}
  \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
\end{equation*}
%% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.

Martingale condition can be rewritten as
\begin{equation*}
  \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
\end{equation*}
which coincides with the result of Santachiara [arXiv:0705.2749].

\subsection{Next steps}
\begin{itemize}
\item Act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations connecting $\kappa, \tau, k$. 
\item Use Knizhnik-Zamolodchikov equations to simplify them.
\item Get conditions on boundary condition changing operator
\item Compare these conditions with results of  the study of boundary states with fusion algebra (Verlinde formula for Cardy states)
\end{itemize}

\section{Conclusion}
\label{sec:conclusion}

\subsection{Conclusion}
\begin{itemize}
\item It is possible to match SLE observables and CFT correlators
\item Martingale conditions are equivalent to Verma module of affine Lie algebra having singular weights at level two.
\item Primary fields of $\gf\oplus \af$ WZNW-model with equivalence relations can be used to study coset theory
\item Study of martingale conditions in coset theory is parallel to the study of boundary states with fusion algebra
\end{itemize}

\subsection{Thank you for your attention!}

@@

\section{Introduction}
SLE for WZW models are actively studied. KZ-equations allow to show that certain functions are martingales. 
In coset models of CFT it is possible to write analogues of KZ equations from null vector conditions. 
Corresponding SLE should have natural interpretation in case of coset construction of minimal models.

SLE is interpreted as limit of interfaces in lattice models. So SLE observable should have the form of boundary correlation function with boundary condition changing operator inserted. There is some condition on spin of boundary condition changing operator in Kostya's paper.  Classification of boundary condition changing operators is given in papers in CFT folder.

What to do:
Simplest coset model: $su(2)_{1}\oplus su(2)_{1}/su(2)_{2}$ $k=1, c=1/2$.

Schramm-Loewner evolution is conformally-invariant probability measure on the continuous curves in complex domain. We work with upper half-plane. SLEs are limits of critical interfaces in lattice models such as Ising model, percolation, FK-model. 
SLE can be used to make a connection with boundary conformal field theory. Observables in presence of SLE (probabilities) are identified with certain correlators in BCFT.

Rational conformal field theories have description in terms of coset models. These models have geometric formulation as gauged WZNW models. Minimal models of CFT can be realized as coset models. So (at least) some of coset models can be seen as the limit of lattice models. 
\section{WZW-models and SLE}
\label{sec:wzw-models-sle}

$SLE_{\kappa,\tau}$ appears in WZW [cite: Gruzberg, Alekseev-Bytsko-Izurov]. Brownian motion on Lie group.

Boundary conditions. Boundary condition changing operators.

\section{Parafermions}
\label{sec:parafermions}

Parafermions are fields in coset $\hat{su}(2)/\hat{u}(1)$. Generalization of Brownian motion. Possible boundary conditions. D-branes.

\section{Coset models}
\label{sec:coset-models}

Boundary conditions??

Ishikava paper - method to get boundary operators.

Ising model - boundary condition changing operator should be known (find).

Generalizations of Brownian motion??

\section{Conclusion}
\label{sec:conclusion}

\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass{article}
\begin{document}
Hello!
It's a pleasure for me to be here in Prague.

My talk is devoted to the correspondence between Schramm-Loewner evolution and conformal field theory.

First of all I need to remind you of Schramm-Loewner evolution.
Consider Ising model on triangular lattice on upper half plane. Let we have spins down on one half of the boundary and spins up on another half. Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity. 
Next we consider continuous limit of lattice model. We can think of it as of stochastic process which satisfy this stochastic equation. Here gt or wt is conformal map which maps SLE trace up to time t to the boundary. 
Now we can look at the observables in the presence of SLE trace. Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace multiplied by the probability of this trajectory. 
Since lattice observable does not depend on the choice of time t, observables in presence of SLE trace should be martingales. 
In continuous limit lattice observable tends to CFT correlation function of this form. It contains some set of primary fields. And we have boundary condition changing operators at the tip of SLE trace and in the infinity. 
We can use conformal map w of z to rewrite this expression in upper half plane. 
Now we want to consider evolution from t to t plus dt. First factor give us this expression. Primary field under conformal map are changed in this way.
We denote generator of this transform by gi.
Now for expectation value of martingale we have this expression. We use Ito calculus to calculate increment of our correlation function. It should be zero so we get this equation.
We can see that it can be rewritten as the action of Virasoro generators. Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state. 
In case of minimal model we can see that boundary condition chaining operator is primary field phi one two or phi two one. 
Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model. The action for this model can be written in terms of map from complex plane with infinity or two-sphere to some Lie group G. 
The first term is just non-linear sigma-model. Here K is Killing form on algebra g. The second term is written in terms of continuation from two sphere to three-dimensional manifold which has two sphere as the boundary. Since this continuation is non-unique we get the requirement for k to be integer. 
Currents of this model have this form. 
Model possess gauge invariance with omega and omega bar in dependant. If we consider infinitesimal gauge transformation we get this Ward identities. Then we can get operator product expansion for currents. 
If we expand currents to modes we get commutation relations of affine Lie algebra g hat. 
This model has conformal invariance which can be seen from 
Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra g hat. 
Full chiral algebra of the model is semidirect product of affine and Virasoro algebra. Its commutation relations are here. 
Primary fields are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields.

Now we want to study Schramm-Loewner evolution in this case. Similarly to minimal case we need to study this correlation function. 
Again we can use conformal map w of z to rewrite it on the whole upper half-plane. 
We consider evolution from time t to t plus dt. We get the same expression from the first factor. But when we consider fields we need to add random gauge transformation. 
Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions. The generator of field transformation have this form. We can interpret last term as Brownian motion in Lie group G.
Then we use Ito calculus to get this equation from martingale condition. Again we can rewrite it as algebraic requirement for  field  which correspond to boundary condition changing operator.
If we act on this state with raising operators we should get zero. We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation. To study this equations we need to use Knizhnik-Zamolodchikov equations. Also we get some constraints on possible boundary condition changing operators.

@@

\end{document}
